The Impact of Tax Policy Evolution on Economic Development and Income Inequality

### 2024-02-19 paper/paper.qmd
Update title

---
title: "Tax-Equity-in-Low-and-Middle-Income-Countries-Replication"
author: 
  - Amie Liu, Wanling Ma
thanks: "Code and data are available at: https://github.com/WanlingMa/Tax-Equity-in-Low-and-Middle-Income-Countries-Replication"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "The Impact of Tax Policy Evolution on Economic Development and Income Inequality"
author: 
  - Amie Liu, Wanling Ma
thanks: "Code and data are available at: https://github.com/WanlingMa/Tax-Equity-in-Low-and-Middle-Income-Countries-Replication"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
